Data_Analysis_exp7

### 2018-07-03 Replication/Results/data_analysis/preproc/Analysis_exp7_rep_prepro.rmd
revise exp1's code

```{r loadingData_e7,,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
# read these files and combine them into one file, get the raw data for matching task
df.M <- read.csv('MS_rep_matchingTask_raw.csv', header=TRUE, sep=",",stringsAsFactors=F)
df.C <- read.csv('MS_rep_categTask_raw.csv', header=TRUE, sep=",",stringsAsFactors=F)
```

>>>>

```{r loadingData_e7,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
# read these files and combine them into one file, get the raw data for matching task
df.M <- read.csv('MS_rep_matchingTask_raw.csv', header=TRUE, sep=",",stringsAsFactors=F)
df.C <- read.csv('MS_rep_categTask_raw.csv', header=TRUE, sep=",",stringsAsFactors=F)
```

### 2018-07-03 Results/Traditional_Analysis/Analysis_exp7_2.rmd
revise exp1's code

```{r Initializing, include=FALSE}
Sys.setlocale("LC_ALL", "English")  # set local encoding to English
Sys.setenv(LANG = "en") # set the feedback language to English
options(scipen = 999)   # force R to output in decimal instead of scientifc notion
options(digits=5)       # limit the number of reporting
rm(list = setdiff(ls(), lsf.str()))  # remove all data but keep functions

pkgTest <- function(x)
 {
   if (!require(x,character.only = TRUE))
  {
    install.packages(x,dep = TRUE)
   if(!require(x,character.only = TRUE)) stop("Package not found")
  }
}

pkgNeeded <- (c("plyr","tidyverse","ggplot2", "reshape2","ez", "bootES","MBESS", "BayesFactor","psych","corrplot"))

lapply(pkgNeeded,pkgTest) # please pay attention to the overlap between differen libraries.
rm(pkgNeeded)             # remove the pkgNeeded variable

# using APA style plot for later use
windowsFonts(Times=windowsFont("TT Times New Roman")) # explicit mapping to "times"
apatheme=theme_bw()+
        theme(panel.grid.major = element_blank(),
              panel.grid.minor = element_blank(),
              panel.background = element_blank(),
              panel.border = element_blank(),
              text=element_text(family='Times'),
              legend.title=element_blank(),
              legend.position='top',
              axis.line.x = element_line(color='black'),
              axis.line.y = element_line(color='black'))

# define the d prime function
dprime <- function(hit,fa) {
        qnorm(hit) - qnorm(fa)
}

## code for calculate the summary with sE, adopted from cook book for R
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
        library(plyr)

        # New version of length which can handle NA's : if na.rm == T, don't count the
        length2 <- function(x, na.rm=FALSE){
                if(na.rm) sum(!is.na(x))
                else      length(x)
        }

        # this does the summary. For each group's data frame, return a vector with
        # N, mean, and sd
        datac <- ddply(data,groupvars, .drop=.drop,
                       .fun = function(xx,col){
                        c(N    = length2(xx[[col]],na.rm=na.rm),
                          mean = mean(xx[[col]],na.rm=na.rm),
                          sd   = sd  (xx[[col]],na.rm=na.rm)
                           )
                       },
                       measurevar
                       )
        # Rename the "mean" column

        datac <- plyr::rename(datac,c("mean" = measurevar))

        datac$se <- datac$sd /sqrt(datac$N)   # calculate standard error of the mean

        # Confidence interval mltiplier for standard error
        # calculate t-statistic for confidence interval:
        # e.g., if conf.interval is .95, use .975 (above/below), and use df.L1 = N-1
        ciMult <- qt(conf.interval/2 + .5, datac$N-1)
        datac$ci <- datac$se * ciMult

        return (datac)
}

## code for calculate the summary with sE for within subject data, adopted from cook book for R
summarySEwithin <- function(data=NULL, measurevar, betweenvars=NULL, withinvars=NULL,idvar=NULL, na.rm=FALSE, conf.interval=.95, .drop=TRUE) {

        # Ensure that the betweenvars and withinvars are factors
        factorvars <- vapply(data[, c(betweenvars, withinvars), drop=FALSE],
                             FUN=is.factor, FUN.VALUE=logical(1))

        if (!all(factorvars)) {
                nonfactorvars <- names(factorvars)[!factorvars]
                message("Automatically converting the following non-factors to factors: ",
                        paste(nonfactorvars, collapse = ", "))
                data[nonfactorvars] <- lapply(data[nonfactorvars], factor)
        }

        # Get the means from the un-normed data
        datac <- summarySE(data, measurevar, groupvars=c(betweenvars, withinvars),
                           na.rm=na.rm, conf.interval=conf.interval, .drop=.drop)

        # Drop all the unused columns (these will be calculated with normed data)
        datac$sd <- NULL
        datac$se <- NULL
        datac$ci <- NULL

        # Norm each subject's data
        ndata <- normDataWithin(data, idvar, measurevar, betweenvars, na.rm, .drop=.drop)

        # This is the name of the new column
        measurevar_n <- paste(measurevar, "_norm", sep="")

        # Collapse the normed data - now we can treat between and within vars the same
        ndatac <- summarySE(ndata, measurevar_n, groupvars=c(betweenvars, withinvars),
                            na.rm=na.rm, conf.interval=conf.interval, .drop=.drop)

        # Apply correction from Morey (2008) to the standard error and confidence interval
        #  Get the product of the number of conditions of within-S variables
        nWithinGroups    <- prod(vapply(ndatac[,withinvars, drop=FALSE], FUN=nlevels,
                                        FUN.VALUE=numeric(1)))
        correctionFactor <- sqrt( nWithinGroups / (nWithinGroups-1) )

        # Apply the correction factor
        ndatac$sd <- ndatac$sd * correctionFactor
        ndatac$se <- ndatac$se * correctionFactor
        ndatac$ci <- ndatac$ci * correctionFactor

        # Combine the un-normed means with the normed results
        merge(datac, ndatac)
}

### code for normalizing the SE
normDataWithin <- function(data=NULL, idvar, measurevar, betweenvars=NULL,
                           na.rm=FALSE, .drop=TRUE) {
        library(plyr)

        # Measure var on left, idvar + between vars on right of formula.
        data.subjMean <- ddply(data, c(idvar, betweenvars), .drop=.drop,
                               .fun = function(xx, col, na.rm) {
                                       c(subjMean = mean(xx[,col], na.rm=na.rm))
                               },
                               measurevar,
                               na.rm
        )

        # Put the subject means with original data
        data <- merge(data, data.subjMean)

        # Get the normalized data in a new column
        measureNormedVar <- paste(measurevar, "_norm", sep="")
        data[,measureNormedVar] <- data[,measurevar] - data[,"subjMean"] +
                mean(data[,measurevar], na.rm=na.rm)

        # Remove this subject mean column
        data$subjMean <- NULL

        return(data)
}

#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
        library(grid)

        # Make a list from the ... arguments and plotlist
        plots <- c(list(...), plotlist)

        numPlots = length(plots)

        # If layout is NULL, then use 'cols' to determine layout
        if (is.null(layout)) {
                # Make the panel
                # ncol: Number of columns of plots
                # nrow: Number of rows needed, calculated from # of cols
                layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                                 ncol = cols, nrow = ceiling(numPlots/cols))
        }

        if (numPlots==1) {
                print(plots[[1]])

        } else {
                # Set up the page
                grid.newpage()
                pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

                # Make each plot, in the correct location
                for (i in 1:numPlots) {
                        # Get the i,j matrix positions of the regions that contain this subplot
                        matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

                        print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                                        layout.pos.col = matchidx$col))
                }
        }
}

@@

# valid data for categorization task
df.T1.V.basic <- df.T1.V[!duplicated(df.T1.V$Subject), 1:4]
numV.female.T <- sum(df.T1.V.basic$Gender == 'female');
numV.male.T <- sum(df.T1.V.basic$Gender == 'male');
ageV.mean.T <- round(mean(df.T1.V.basic$Age),2);
ageV.std.T <- round(sd(df.T1.V.basic$Age),2);
ratio.excld.trials.T <- nrow(excld.trials.T)/nrow(df.T1.valid)
```
## Participants
`r numT.subj+length(procFailureSub)` college students (`r numT.female` female, age: `r ageT.mean` $\pm$ `r ageT.std`) participated in experiment 7. All partcipants were right handed, and all had normal or corrected-to-normal vision. Informed consent was obtained from all partcipants prior to the experiment according to procedure approved by a local ethics committee. Data of `r length(procFailureSub)` participants were excluded from matching task because of the procedura failure, and `r num.excld.sub` of the participants data were excluded from the analysis for matching task and categorization task because of less than 50% overall accuracy for the matching task, leaving `r numT.subj - num.excld.sub` participants (`r numV.female` female, age: `r ageV.mean` $\pm$ `r ageV.std` years) for matching task. `r num.excld.sub.T` addtional participants's data in categorization task were excluded becasue of less than 50% accuracy for the categorization task,leaving `r numT.subj - num.excld.sub - num.excld.sub.T` participants (`r numV.female.T` female, age: `r ageV.mean.T` $\pm$ `r ageV.std.T` years) for categorization task.

@@

>>>>

```{r Initializing, include=FALSE}
source('Initial.r')
curDir <- getwd()   # directory for preprocessing
rootDir <- gsub('.{7}$', '', curDir)
#rawDir <- paste(curDir,'/data/',sep = '')
traDir <- paste(rootDir,'Traditional_Analysis',sep = '')
ddmDir <- paste(rootDir,'HDDM',sep = '')
```

@@

# valid data for categorization task
df.T1.V.basic <- df.T1.V[!duplicated(df.T1.V$Subject), 1:4]
numV.female.T <- sum(df.T1.V.basic$Gender == 'female');
numV.male.T <- sum(df.T1.V.basic$Gender == 'male');
ageV.mean.T <- round(mean(df.T1.V.basic$Age),2);
ageV.std.T <- round(sd(df.T1.V.basic$Age),2);
ratio.excld.trials.T <- nrow(excld.trials.T)/nrow(df.T1.valid)

# get the data file for hddm analysis

df.L.ddm.v <- df.L[!(df.L$Subject %in% c(procFailureSub,excld.sub)),]   # exclude the invalid subjects

df.T.ddm.v <- df.T[!(df.T$Subject %in% c(procFailureSub,excld.sub)),]
df.T.ddm.v <- df.T.ddm.v[!(df.T.ddm.v$Subject %in% excld.sub.T),]
df.T.ddm.v <- df.T[df.T$Task != 'importance',]  # exclude the results from importance task

#df.L1 <- df.L1[!(df.L1$Subject %in% procFailureSub),]
#df.T1 <- df.T1[!(df.T1$Subject %in% procFailureSub),]

#df.L1.valid <- df.L1.fm[!(df.L1.fm$Subject %in% excld.sub),]
#df.T1.valid <- df.T1[!(df.T1$Subject %in% excld.sub),]
#df.T1.valid <- df.T1.valid[!(df.T1.valid$Subject %in% excld.sub.T),]

df.L.hddm <- subset(df.L.ddm.v, ACC ==1 | ACC == 0)  # remove non-response trials or pressing wrong key
df.T.hddm <- subset(df.T.ddm.v, ACC ==1 | ACC == 0)

df.L.hddm_m <- subset(df.L.hddm, Match == 'match') # select data
df.L.hddm_m <- df.L.hddm_m[,c('Subject','Morality','Identity','RT','ACC')] # select column
colnames(df.L.hddm_m) <- c("subj_idx","val",'id','rt','response')     # change column name

df.L.hddm_nm <- subset(df.L.hddm, Match == 'mismatch')
df.L.hddm_nm <- df.L.hddm_nm[,c('Subject','Morality','Identity','RT','ACC')]
colnames(df.L.hddm_nm) <- c("subj_idx","val",'id','rt','response')

df.T.hddm_val <- subset(df.T.hddm, Task == 'Val')
df.T.hddm_val <- df.T.hddm_val[,c('Subject','Morality','Identity','RT','ACC')]
colnames(df.T.hddm_val) <- c("subj_idx","val",'id','rt','response')

df.T.hddm_id <- subset(df.T.hddm, Task == 'Id')
df.T.hddm_id <- df.T.hddm_id[,c('Subject','Morality','Identity','RT','ACC')]
colnames(df.T.hddm_id) <- c("subj_idx","val",'id','rt','response')

setwd(ddmDir)
write.csv(df.L.hddm_m,'exp7_rep_match_hddm.csv',row.names = F)
write.csv(df.L.hddm_nm,'exp7_rep_mismatch_hddm.csv',row.names = F)
write.csv(df.T.hddm_val,'exp7_rep_categ_val_hddm.csv',row.names = F)
write.csv(df.T.hddm_id,'exp7_rep_categ_id_hddm.csv',row.names = F)
rm('df.L.hddm','df.T.hddm','df.L.hddm_m','df.L.hddm_nm','df.T.hddm_val','df.T.hddm_id')
setwd(curDir)
```
## Participants
`r numT.subj+length(procFailureSub)` college students (`r numT.female` female, age: `r ageT.mean` $\pm$ `r ageT.std`) participated in experiment 7. All partcipants were right handed, and all had normal or corrected-to-normal vision. Informed consent was obtained from all partcipants prior to the experiment according to procedure approved by a local ethics committee. Data of `r length(procFailureSub)` participants were excluded from matching task because of the procedura failure, and `r num.excld.sub` of the participants data were excluded from the analysis for matching task and categorization task because of less than 50% overall accuracy for the matching task, leaving `r numT.subj - num.excld.sub` participants (`r numV.female` female, age: `r ageV.mean` $\pm$ `r ageV.std` years) for matching task. `r num.excld.sub.T` addtional participants's data in categorization task were excluded becasue of less than 50% accuracy for the categorization task,leaving `r numT.subj - num.excld.sub - num.excld.sub.T` participants (`r numV.female.T` female, age: `r ageV.mean.T` $\pm$ `r ageV.std.T` years) for categorization task.

@@

MSplots(saveDir = traDir, curDir = curDir, task = 'match',type = 'dprime', inData = df.M1.V.SDT_l)
